Forecast of the 2024 Presidential Election through the Lens of Turbulent Battleground States

### 2024-11-04 paper/paper.qmd

---
title: "Forecast of the 2024 Presidential Election through the Lens of Turbulent Battleground States"
subtitle: "Kamala Harris Leads the Race With 276 Electoral Votes With Support in 3 of 4 Swing States"
author: 
  - Andy Jiang
  - Onon Burentuvshin
  - Rui Hu
thanks: "Code and data are available at: [https://github.com/AndyYanxunJiang/president-polls)."
date: today
date-format: long
abstract: "The 2024 U.S. presidential election is shaping up to be a highly swing race, with polling data playing a crucial role in gauging public sentiment and forecasting the potential outcome. This paper builds a predictive model using a poll-of-polls approach, aggregating data from multiple pollsters to forecast the winner of the upcoming election. The analysis incorporates polling data from various sources, filtered to include only high-quality pollsters with a numeric grade above 3, to ensure the reliability of the predictions. By incorporating the poll-of-polls approach with our model, we predict that Kamla Harris edges our Trump in the presidential election. Our model forecasts that with a 1%-4% margin lead in Pennsylvania, Wisconsin, Nevada, and Michigan, Kamala Harris will accumulate 276 electoral votes to win the election. Additionally, a detailed examination of one selected pollster’s methodology is conducted, highlighting strengths, weaknesses, and biases in the survey process. The paper concludes with an idealized polling methodology, designed within a $100K budget, to enhance the accuracy of election forecasts. Results are presented in the context of understanding polling trends, potential biases, and the evolving landscape of voter preferences as the election approaches."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Appendix B {-}

@@

###   Referral Mechanics
To further broaden our reach without exponentially increasing advertising costs, we incorporate a referral system that rewards respondents for inviting others to complete the survey [@tellingstories]. Each referral allows the original respondent to gain an additional entry in the lottery, increasing their chances of winning. This referral incentive taps into snowball sampling, where respondents refer people within their network to participate, expanding our pool of respondents organically.
However, using snowball sampling in an election survey introduces potential biases, particularly the risk of overrepresentation of individuals with similar political views, as respondents are likely to refer to close contacts who may share similar ideologies. To mitigate this, we will place specific restrictions on the referral program. Each respondent will be limited to referring only one other individual, minimizing the potential for overly clustered referrals. Additionally, we will require respondents to identify their relationship with each referral, helping us monitor homogeneity in our responses. By balancing the benefits of snowball sampling with these restrictions, we aim to expand the reach of our survey into difficult to reach demographics without compromising the representativeness of the sample.

@@

\includepdf[pages=-]{..other/datasheet/Poll Survey - Google Forms.pdf}

>>>>

---
title: "Forecast of the 2024 Presidential Election through the Lens of Turbulent Battleground States"
subtitle: "Kamala Harris Leads the Race With 276 Electoral Votes With Support in 3 of 4 Swing States"
author: 
  - Andy Jiang
  - Onon Burentuvshin
  - Rui Hu
thanks: "Code and data are available at: [https://github.com/AndyYanxunJiang/president-polls)."
date: today
date-format: long
abstract: "The 2024 U.S. presidential election is shaping up to be a highly swing race, with polling data playing a crucial role in gauging public sentiment and forecasting the potential outcome. This paper builds a predictive model using a poll-of-polls approach, aggregating data from multiple pollsters to forecast the winner of the upcoming election. The analysis incorporates polling data from various sources, filtered to include only high-quality pollsters with a numeric grade above 3, to ensure the reliability of the predictions. By incorporating the poll-of-polls approach with our model, we predict that Kamla Harris edges our Trump in the presidential election. Our model forecasts that with a 1%-4% margin lead in Pennsylvania, Wisconsin, Nevada, and Michigan, Kamala Harris will accumulate 276 electoral votes to win the election. Additionally, a detailed examination of one selected pollster’s methodology is conducted, highlighting strengths, weaknesses, and biases in the survey process. The paper concludes with an idealized polling methodology, designed within a $100K budget, to enhance the accuracy of election forecasts. Results are presented in the context of understanding polling trends, potential biases, and the evolving landscape of voter preferences as the election approaches."
format: pdf
number-sections: true
bibliography: references.bib
header-includes:
  - \usepackage{pdfpages}
---

@@

@@

###   Referral Mechanics
To further broaden our reach without exponentially increasing advertising costs, we incorporate a referral system that rewards respondents for inviting others to complete the survey [@tellingstories]. Each referral allows the original respondent to gain an additional entry in the lottery, increasing their chances of winning. This referral incentive taps into snowball sampling, where respondents refer people within their network to participate, expanding our pool of respondents organically.

However, using snowball sampling in an election survey introduces potential biases, particularly the risk of overrepresentation of individuals with similar political views, as respondents are likely to refer to close contacts who may share similar ideologies. To mitigate this, we will place specific restrictions on the referral program. Each respondent will be limited to referring only one other individual, minimizing the potential for overly clustered referrals. Additionally, we will require respondents to identify their relationship with each referral, helping us monitor homogeneity in our responses. By balancing the benefits of snowball sampling with these restrictions, we aim to expand the reach of our survey into difficult to reach demographics without compromising the representativeness of the sample.

@@
